Super-resolution of Aeromagnetic Survey Data

### 2023-10-11 discussion.tex
Short titles for figures, fix cites

\begin{figure}
    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
    \caption{
        A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
        a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{}+ Network, d) The ESRGAN+ network, and e) The LTE network.}
    \label{fig:modcomp}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
    \caption[Comparison between the three SR architectures]{
        A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
        a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{}+ Network, d) The ESRGAN+ network, and e) The LTE network.}
    \label{fig:modcomp}
\end{figure}

### 2023-10-11 intro.tex
Short titles for figures, fix cites

The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
Potential field surveys offer low-cost investigations over a large spatial extent, and are routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
Scattered surveys are commonly interpolated to grid rasters, and interpreted individually or integrated with other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2018}.
The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however, it is not understood if these methods can extend to geophysics data, which differ significantly to the natural images used for training in prior enhancement methods.

@@

There are many aspects of survey design controlling the resolvable detail within survey data.
When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
Higher frequencies within potential field data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
Surveys are flown with a heading in which data will be acquired along line.
For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
The spacing between lines is a factor of the scale of investigation and the cost of acquisition, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
Survey cost rapidly increases when surveying at higher resolution, due to overheads in flight line sampling.
Higher-resolution surveys over prospective areas fly lines at closer line spacings, of the order \qty{100}{\m}, in order to resolve greater detail.
The importance of these parameters in relation to resolvable detail will be outlined shortly.
The collected data may contain millions of samples scattered in three dimensions, and interpretation or processing often relies on regularisation to a quantised grid.

@@

\subsection{A definition for geophysical resolution}
In interpolated grids the spatial dimension of each cell is referred to as the cell size.
As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
Height is controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2018,reidAeromagneticSurveyDesign1980}.
Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of one third to one fifth the line spacing.
This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
If the sampling frequency is nominally \qty{7}{\m} in the flight line direction, and up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.

@@

Early adoption of SR was seen in satellite and airborne remote sensing, where the data share image features with natural images \parencite{lanarasSuperresolutionSentinel2Images2018,arunConvolutionalNetworkArchitectures2019,kawulokTrainingDeepNetworks2019}, and others.
Hyperspectral data SR are commonly investigated \parencite{yangHyperspectralImageClassification2018,arunCNNBasedSuperResolutionHyperspectral2020}.
Rock microscopy images have been upsampled with SR \parencite{niuInnovativeApplicationGenerative2020}, and their accuracy compared using domain specific parameter calculation.
SR with physics-informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
Additionally, physics-informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and SR with the removal of noise \parencite{liDeepLearningSimultaneous2021}.

>>>>

The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
Potential field surveys offer low-cost investigations over a large spatial extent, and are routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
Scattered surveys are commonly interpolated to grid rasters, and interpreted individually or integrated with other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2013}.
The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however, it is not understood if these methods can extend to geophysics data, which differ significantly to the natural images used for training in prior enhancement methods.

@@

There are many aspects of survey design controlling the resolvable detail within survey data.
When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
Higher frequencies within potential field data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
Surveys are flown with a heading in which data will be acquired along line.
For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2013}.
Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
The spacing between lines is a factor of the scale of investigation and the cost of acquisition, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
Survey cost rapidly increases when surveying at higher resolution, due to overheads in flight line sampling.
Higher-resolution surveys over prospective areas fly lines at closer line spacings, of the order \qty{100}{\m}, in order to resolve greater detail.
The importance of these parameters in relation to resolvable detail will be outlined shortly.
The collected data may contain millions of samples scattered in three dimensions, and interpretation or processing often relies on regularisation to a quantised grid.

@@

\subsection{A definition for geophysical resolution}
In interpolated grids the spatial dimension of each cell is referred to as the cell size.
As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2013,dentithGeophysicsMineralExploration2014}.
Height is controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2013,reidAeromagneticSurveyDesign1980}.
Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of one third to one fifth the line spacing.
This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
If the sampling frequency is nominally \qty{7}{\m} in the flight line direction, and up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.

@@

Early adoption of SR was seen in satellite and airborne remote sensing, where the data share image features with natural images \parencite{lanarasSuperresolutionSentinel2Images2018,arunConvolutionalNetworkArchitectures2019,kawulokTrainingDeepNetworks2019}, and others.
Hyperspectral data SR are commonly investigated \parencite{yangHyperspectralImageClassification2018,arunCNNBasedSuperResolutionHyperspectral2020}.
Rock microscopy images have been upsampled with SR \parencite{niuInnovativeApplicationGenerative2020}, and their accuracy compared using domain specific parameter calculation.
SR with physics-informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsconstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
Additionally, physics-informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and SR with the removal of noise \parencite{liDeepLearningSimultaneous2021}.

### 2023-10-11 paper1.tex
Short titles for figures, fix cites

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p1/rdb.png}
    \caption[Basic Blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
        Noise injection is not used in RDN\@.
        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:rdb}
\end{figure}

@@

\subsection{Accuracy metrics}
The functional aim of super-resolution geophysics is to accurately predict realistic high frequency details to add to a low-resolution grid.
To quantify this, we calculate root mean square error (RMSE) and structural similarity metrics (SSIM and MS-SSIM), on TMI, high pass filtered TMI, and first vertical derivative (1VD) filtered TMI results for each upsampling method across several sample extents.
Euclidean accuracy measures like RMSE quantify the per-pixel accuracy of a predicted grid compared to its corresponding high-resolution ground truth grid.
For this metric, quality improves as the error value approaches \num{0}.
The Structural Similarity (SSIM) \parencite{wangImageQualityAssessment2004} and Multi-Scale Structural Similarity (MSSSIM) \parencite{wangMultiscaleStructuralSimilarity2003} image quality metrics use sliding windows to quantify image perceptual similarity based on localised structural information.
MS-SSIM extends SSIM by performing a weighted sum of the measure at several different scales.
In both structural metrics, the result is a combination of localised image luminance, contrast, and structural information.
A SSIM value of 1 indicates perfect similarity, and values approaching \num{0} indicate increasing dissimilarity.

\section{Results}
Results are presented to compare the three methods described above, with the metrics of RMSE, SSIM and MS-SSIM, as well as observed perceptual quality.
In addition to unfiltered TMI comparisons, high pass filtered and first vertical derivative TMI grids are also shown.
These products are commonly used in geophysics to investigate high frequency components in grids.

@@

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
    \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \Cref{fig:trainvaldata}.
        The Nyquist wavelengths for the high-resolution (and upsampled) rasters and low-resolution raster are also shown.
        The frequency axis has been transformed to wavelength, and the spectra have been normalised for direct comparison.
        Note the complete test extent is covered by surveys with a range of line spacings from \qty{100}{\metre} to \qty{20}{\metre}, with \qty{100}{\metre} being the most extensive.
        The Nyquist wavelength of the \qty{100}{\metre} surveys (optimal grid cell size approximately \qty{20}{\metre}) likely causes the reduction in power at \qty{55}{\metre} and \qty{220}{\metre}.
    }
    \label{fig:rapsd}
\end{figure}

To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\Cref{fig:filtered}). Bicubic interpolation (\Cref{fig:filtered} c) fails to add significant high frequency components.
RDN\textdaggerdbl{} (\Cref{fig:filtered} d) appears to approximate similar high frequencies to the HR tile (\Cref{fig:filtered} b), while ESRGAN+ (\Cref{fig:filtered} e) shows potentially excessive predicted high frequency components.
Finally, metrics for the full set of test tiles are reported in \Cref{tab:metrics}.
The non-GAN CNN approach of RDN\textdaggerdbl{} remains the most accurate method for the entire test grid.
Several routinely occurring artefacts are observed in the two super-resolution products, especially in ESRGAN+ which incorporates details it has learned from the Discriminator network loss.
The First Vertical Derivative filter is used in \Cref{fig:jhillvis} to demonstrate the ability to perform common geophysical filters on super resolved grids, and to emphasise examples of these artefacts.
The most apparent artefact arises from the inference implementation when upsampling a grid larger than fits in memory, where visible edges appear around individual tiles in the compiled inference grid (e.g. \Cref{fig:jhillvis}, *).
This could be reduced by adjusting the size of inference tiles, or slightly overlapping adjacent input tiles.
Predictions from ESRGAN+ commonly show a ripple-like texture (\Cref{fig:jhillvis}, \^{ }), especially around pronounced high TMI features.
The effect of this texture occasionally reveals features matching the high-resolution groundtruth that are not predicted by the bicubic or RDN\textdaggerdbl{} upsampling, but the excess of “noisy” features present in ESRGAN+ predictions will likely limit its applicability when interpreting low-resolution grids with no corresponding groundtruth.

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
    \caption[High Pass filtered results]{High pass filtered test tile and its upsampled counterparts.
        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
    }
    \label{fig:filtered}
\end{figure}

@@

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/1vd.jpg}
    \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
    Red asterisks (*) show a vertical tile boundary present as a 3--4 pixel-wide error in predicted TMI value.
    Red caret (\^{ }) indicates a region of subtle ripple-mark textural artefact, only present in ESRGAN+ predictions.
    }
    \label{fig:jhillvis}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/jhilldykes.png}
    \centering
    \includegraphics[width=0.7\linewidth]{fig/p1/transectp.png}
    \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).
        Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \qty{650}{\metre} and \qty{1020}{\metre}.
    }
    \label{fig:jhilldykes}
\end{figure}

>>>>

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p1/rdb.png}
    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
        Noise injection is not used in RDN\@.
        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:rdb}
\end{figure}

@@

\subsection{Accuracy metrics}
The functional aim of super-resolution geophysics is to accurately predict realistic high frequency details to add to a low-resolution grid.
To quantify this, we calculate root mean square error (RMSE) and structural similarity metrics (SSIM and MS-SSIM), on TMI, high-pass filtered TMI, and first vertical derivative (1VD) filtered TMI results for each upsampling method across several sample extents.
Euclidean accuracy measures like RMSE quantify the per-pixel accuracy of a predicted grid compared to its corresponding high-resolution ground truth grid.
For this metric, quality improves as the error value approaches \num{0}.
The Structural Similarity (SSIM) \parencite{wangImageQualityAssessment2004} and Multi-Scale Structural Similarity (MSSSIM) \parencite{wangMultiscaleStructuralSimilarity2003} image quality metrics use sliding windows to quantify image perceptual similarity based on localised structural information.
MS-SSIM extends SSIM by performing a weighted sum of the measure at several different scales.
In both structural metrics, the result is a combination of localised image luminance, contrast, and structural information.
A SSIM value of 1 indicates perfect similarity, and values approaching \num{0} indicate increasing dissimilarity.

\section{Results}
Results are presented to compare the three methods described above, with the metrics of RMSE, SSIM and MS-SSIM, as well as observed perceptual quality.
In addition to unfiltered TMI comparisons, high-pass filtered and first vertical derivative TMI grids are also shown.
These products are commonly used in geophysics to investigate high frequency components in grids.

@@

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
    \caption[Power spectra for the test extent]{Radially Averaged Power Spectra for the complete test extent shown in \Cref{fig:trainvaldata}.
        The Nyquist wavelengths for the high-resolution (and upsampled) rasters and low-resolution raster are also shown.
        The frequency axis has been transformed to wavelength, and the spectra have been normalised for direct comparison.
        Note the complete test extent is covered by surveys with a range of line spacings from \qty{100}{\metre} to \qty{20}{\metre}, with \qty{100}{\metre} being the most extensive.
        The Nyquist wavelength of the \qty{100}{\metre} surveys (optimal grid cell size approximately \qty{20}{\metre}) likely causes the reduction in power at \qty{55}{\metre} and \qty{220}{\metre}.
    }
    \label{fig:rapsd}
\end{figure}

To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high-pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\Cref{fig:filtered}). Bicubic interpolation (\Cref{fig:filtered} c) fails to add significant high frequency components.
RDN\textdaggerdbl{} (\Cref{fig:filtered} d) appears to approximate similar high frequencies to the HR tile (\Cref{fig:filtered} b), while ESRGAN+ (\Cref{fig:filtered} e) shows potentially excessive predicted high frequency components.
Finally, metrics for the full set of test tiles are reported in \Cref{tab:metrics}.
The non-GAN CNN approach of RDN\textdaggerdbl{} remains the most accurate method for the entire test grid.
Several routinely occurring artefacts are observed in the two super-resolution products, especially in ESRGAN+ which incorporates details it has learned from the Discriminator network loss.
The First Vertical Derivative filter is used in \Cref{fig:jhillvis} to demonstrate the ability to perform common geophysical filters on super resolved grids, and to emphasise examples of these artefacts.
The most apparent artefact arises from the inference implementation when upsampling a grid larger than fits in memory, where visible edges appear around individual tiles in the compiled inference grid (e.g. \Cref{fig:jhillvis}, *).
This could be reduced by adjusting the size of inference tiles, or slightly overlapping adjacent input tiles.
Predictions from ESRGAN+ commonly show a ripple-like texture (\Cref{fig:jhillvis}, \^{ }), especially around pronounced high TMI features.
The effect of this texture occasionally reveals features matching the high-resolution groundtruth that are not predicted by the bicubic or RDN\textdaggerdbl{} upsampling, but the excess of “noisy” features present in ESRGAN+ predictions will likely limit its applicability when interpreting low-resolution grids with no corresponding groundtruth.

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
    \caption[High-pass filtered results]{High-pass filtered test tile and its upsampled counterparts.
        The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
    }
    \label{fig:filtered}
\end{figure}

@@

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/1vd.jpg}
    \caption[First vertical derivative over the case study grid]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
    Red asterisks (*) show a vertical tile boundary present as a 3--4 pixel-wide error in predicted TMI value.
    Red caret (\^{ }) indicates a region of subtle ripple-mark textural artefact, only present in ESRGAN+ predictions.
    }
    \label{fig:jhillvis}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/jhilldykes.png}
    \centering
    \includegraphics[width=0.7\linewidth]{fig/p1/transectp.png}
    \caption[Case study TMI grids and line profiles]{Jasper Hills Project TMI grids (a--e) and line profile (f).
        Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \qty{650}{\metre} and \qty{1020}{\metre}.
    }
    \label{fig:jhilldykes}
\end{figure}

### 2023-10-11 paper2.tex
Short titles for figures, fix cites

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
    \caption[The LTE network]{
        A simplified representation of the super-resolution LTE network.
        The encoder is marked as \(E_\phi{}\).
        \(f_\Theta{}\) is an MLP network used as the decoder for image reconstruction.
        A long-range skip connection with simple upscaling is marked with an arrow.
        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
        Simplified from \textcite{leeLocalTextureEstimator2022}.
    }
    \label{fig:ltenet}
\end{figure}

@@

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata23}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata14}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata17}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata18}
\end{figure}

>>>>

\begin{figure}[hbtp]
    \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
    \caption[The LTE architecture]{
        A simplified representation of the super-resolution LTE network.
        The encoder is marked as \(E_\phi{}\).
        \(f_\Theta{}\) is an MLP network used as the decoder for image reconstruction.
        A long-range skip connection with simple upscaling is marked with an arrow.
        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
        Simplified from \textcite{leeLocalTextureEstimator2022}.
    }
    \label{fig:ltenet}
\end{figure}

@@

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
    \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata23}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
    \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata14}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
    \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata17}
\end{figure}

\begin{figure}[hbtp]
    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
    \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
        Explanation in-text.
        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
    \label{fig:srdata18}
\end{figure}
